Cytoscape~可以接受很多命令行参数，包括指定网络文件、属性文件和会话文件。下面的内容是用
Cytoscape~的“-h”或“--help”运行参数得到的：
\begin{verbatim}
usage: java -Xmx512M -jar cytoscape.jar [OPTIONS]
 -h,--help               Print this message.
 -v,--version            Print the version number.
 -s,--session <file>     Load a cytoscape session (.cys) file.
 -N,--network <file>     Load a network file (any format).
 -e,--edge-attrs <file>  Load an edge attributes file (edge attribute format).
 -n,--node-attrs <file>  Load a node attributes file (node attribute format).
 -m,--matrix <file>      Load a node attribute matrix file (table).
 -p,--plugin <file>      Load a plugin jar file, directory of jar files,
                         plugin class name, or plugin jar URL.
 -P,--props <file>       Load cytoscape properties file (Java properties
                         format) or individual property: -P name=value.
 -V,--vizmap <file>      Load vizmap properties file (Java properties format).
\end{verbatim}

在指定文件时，可以是本地文件的路径，也可以是URL。例如，可以这样指定本地的网络文件（假
设myNet.sif位于当前工作目录）：cytoscape.sh -N myNet.sif。还可以用URL指定网络：
cytoscape.sh -N http://example.com/myNet.sif。
\begin{description}
\item[参数] 用途
\item[-h,--help] 显示上面已经展示过的帮助信息，然后退出程序。
\item[-v,--version] 显示~Cytoscape~的版本号，然后退出程序。
\item[-s,--session $<$file$>$] This option specifies a session file to be loaded. 
Since only one session file can be loaded at a given time, this option may only specified once on a given
command line. The option expects a .cys Cytoscape session file. It is customary,
although not necessary, for session file names to contain the .cys extension.
\item[-N,--network $<$file$>$]This option is used to load all types of network files. SIF, GML, and XGMML files
can all be loaded using the -N option. You can specify as many networks as
desired on a single command line.
\item[-e,--edge-attrs $<$file$>$] This option specifies an edge attributes file. You may specify as many edge
attribute files as desired on a single command line.
\item[-n,--node-attrs $<$file$>$] This option specifies a node attributes file. You may specify as many node
attribute files as desired on a single command line.
\item[-m,--matrix $<$file$>$]This option specifies a data matrix file. In a biological context, the data
matrix consists of expression data. All data matrix files are read into node
attributes. You may specify as many data matrix files as desired on a single
command line.
\item[-p,--plugin $<$file$>$]This option specifies a cytoscape plugin (.jar) file to be loaded by Cytoscape.
This option also subsumes the previous "resource plugin option". You may specify
a class name that identifies your plugin and the plugin will be loaded if the
plugin is in Cytoscape's CLASSPATH. For example, assuming that the class MyPlugin
can be found in the CLASSPATH, you could specify the plugin like this:
cytoscape.sh -p MyPlugin.class. A final means of specifying plugins is to specify
a file name whose contents contain a list of plugin jar files.
\item[-P,--props $<$file$>$]This option specifies Cytoscape properties. Properties can be specified either as
a properties file (in Java's standard properties format), or as individual
properties. To specify individual properties, you must specify the property name
followed by the property value where the name and value are separated by the '='
sign. For example to specify the defaultSpeciesName: cytoscape.sh -P
defaultSpeciesName=Human. If you would like to include spaces in your property,
simply enclose the name and value in quotation marks: cytoscape.sh -P
"defaultSpeciesName=Homo Sapiens". The property option subsumes previous options
-noCanonicalization, -species, and -bioDataServer. Now it would look like:
cytoscape.sh -P defaultSpeciesName=Human -P noCanonicalization=true -P
bioDataServer=myServer.
\item[-V,--vizmap $<$file$>$] This option specifies a visual properties file.
\end{description}


All options described above (including plugins) can be loaded from the GUI once
Cytoscape is running.